Whats reported in the news?

### 2018-02-20 paper/R/04_Modelresults.Rmd
inspect k=40

```{r echo = FALSE}
load("../output/models/STM 35 .Rda")
k <- stmOut$settings$dim$K
```

@@

sagelabs$cov.betas[[2]]$problabels[,1:4]
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
                   5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
                   9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
                   11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
                   14, "B90/Die Grüne", 
                   15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
                   18, "Budget statistics, Welfare policy", 
                   19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
                   22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
                   25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
                   27, "Surveys, public statistics", 28, "Election polls", 
                   29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                   34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)

@@

```{r fig.height=11, fig.width=5}
topic <- 3

@@

@@

```{r}
library(radarchart)
```

@@

```{r}
keep <- c(1,2,3,6,8,14,16,17,24,29)
```

#### Unweighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(sent_value = mean(sent_value)) %>%
  spread(key=site, value=sent_value) %>%
  ungroup() -> radar
```

```{r}
chartJSRadar(scores = radar, labelSize = 8, 
             scaleStartValue = -0.2,
             maxScale = 0.1, 
             showToolTipLabel = TRUE,
             width = 8, height = 8)
```

#### Weighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(weighted = mean(weighted)) %>%
  spread(key=site, value=weighted) %>%
  ungroup() -> radar
```

```{r}
chartJSRadar(scores = radar, labelSize = 8, 
             scaleStartValue = -0.005,
             maxScale = 0.002, 
             showToolTipLabel = TRUE,
             width = 8, height = 8)
```

>>>>

```{r echo = FALSE}
load("../output/models/STM 40 .Rda")
k <- stmOut$settings$dim$K
```

@@

sagelabs$cov.betas[[3]]$problabels[,1:5]
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 4, "EU policies", 
                   5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
                   9, "Welt, Deutschland, Menschen", 10, "Parliament (Bundestag)", 
                   11, "W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
                   14, "B90/Die Grüne, climate/refugee policy", 
                   15, "D.Trump, Israel", 16, "Great coalition", 17, "AfD, in media", 
                   18, "Jamaica coalition", 
                   19, "Rubbish", 20, "Terror attack Amri", 21, "German armed forces, Mali, Helicopter", 
                   22, "Muslim, Ditib", 23, "Elections in Niedersachsen", 24, "CDU, Twitter, Saxony", 
                   25, "Europa", 26, "Bundestag, Laws", 
                   27, "Surveys, public statistics", 28, "Election polls", 
                   29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                   34, "Left- & Right-wing Terror", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church", 37, "Car industry, Stuttgart", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

# topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "Jamaica coalition", 4, "Diesel scandal", 
#                    5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
#                    9, "Deportation, radicalization, refugees", 10, "Parliament (Bundestag)", 
#                    11, "DIE LINKE, W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
#                    14, "B90/Die Grüne", 
#                    15, "D.Trump, antisemitism", 16, "Great coalition", 17, "AfD, in social media", 
#                    18, "Budget statistics, Welfare policy", 
#                    19, "Rubbish", 20, "Verfassungsschutz, Terror attacks", 21, "German armed forces, Drones, Mali", 
#                    22, "EU policies, Weather", 23, "Elections in Niedersachsen", 24, "CDU, social media", 
#                    25, "Political talkshows", 26, "Bundestag, Steinmeier, Maas", 
#                    27, "Surveys, public statistics", 28, "Election polls", 
#                    29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
#                    32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
#                    34, "Terror attacks, polics reports", 35, "CDU/CSU H.Seehofer, Obergrenze"), ncol=2, byrow=T)

@@

```{r fig.height=11, fig.width=5}
topic <- 12

@@

```{r}
sentDF.red %>% group_by(topic_name) %>%
  top_n(5, gamma) %>%
  select(topic_name, gamma, title) %>%
  htmlTable::htmlTable(align="l")
```

@@

```{r message=FALSE, warning=FALSE}
require(ggiraph)
require(ggiraphExtra)
```

@@

1, "SPD, M.Schulz"
2, "A.Merkel vs. Schulz"
3, "B90/Die Grüne, coalition talks"
4, "EU policies"
5, "H.Kohl", 
6, "A.Merkel", 
8, "CSU, Seehofer, Söder",
12, "Refugees in GER"
14, "B90/Die Grüne, climate/refugee policy",
16, "Great coalition", 
17, "AfD, in media", 
18, "Jamaica coalition",
29, "AfD",
33, "Diplomatic relations w Turkey, Russia",
35, "CDU/CSU H.Seehofer, Obergrenze",
38, "AfD, F.Petry")

```{r}
#keep <- c(1,2,3,6,8,14,16,17,24,29)

keep <- c(1,3,4,5,6,8,14,16,17,18,29,33,35,38)
```

#### Unweighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(sent_value = mean(sent_value)) %>%
  spread(key=topic_name, value=sent_value) %>%
  ungroup() -> radar

radar %>%
  ggRadar(aes(color=site), rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "")
```

#### Weighted
```{r}
sentDF.red %>% 
  filter(topic %in% keep) %>%
  group_by(site, topic_name) %>%
  summarise(weighted = mean(weighted)) %>%
  spread(key=topic_name, value=weighted) %>%
  ungroup() -> radar

radar %>%
  ggRadar(aes(color=site), rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "")
```
